---
title: "Replicate"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("code/R/auxiliary/packages.r")  # Load required packages
source("code/R/auxiliary/functions.r") # Load additional functions
```

## Introduction

This file replicates all the figures, tables and numbers in "Forecasting Elections in Multi-Party Systems: A Bayesian Approach Combining Polls and Fundamentals" (Stoetzer et al 2018). As re-running all the models can be time consuming, this file takes the MCMC draws in the dataverse and reproduces the Figures and Numbers in the main text as well as all the Figures, Tables and Numbers in the Supplementary Materials. If you run the setup chunk all the necessary packages to replicate the results will be installed and loaded. 

If you want to re-run our models 
The Stan code for the models can be found in ... All the data we used to estimate our models is stored in ...

## R Environment

This code was last tested and run on 6 June 2018.
               _                           
platform       x86_64-apple-darwin15.6.0   
arch           x86_64                      
os             darwin15.6.0                
system         x86_64, darwin15.6.0        
status                                     
major          3                           
minor          4.3                         
year           2017                        
month          11                          
day            30                          
svn rev        73796                       
language       R                           
version.string R version 3.4.3 (2017-11-30)
nickname       Kite-Eating Tree    

RStudio        1.1.383


## Dataverse Structure

## Questions

If you have any further questions or encounter issues while replicating the results please let us know via email to either (or both) Marcel Neunhoeffer or Lukas F. Stoetzer. 

## Replication - Article

The following code chunks will replicate the figures, numbers and tables from the main text and the Supplementary Materials.

### Final Forecast in Text (p. 5)

```{r Final Forecast in Text}
# Final Forecast in Text

df <- readRDS(file="output/ger/draws/combined_model/draws_forcast_levels_2017_2.RDS")

forecast <- df$forecast

colnames(forecast) <- df$party_names

adjustOrder <- match(c("cdu", "spd", "lin", "gru", "fdp", "afd", "oth"), df$party_names)


forecast <- forecast[, adjustOrder]

# Mean Forecast
round(apply(forecast, 2, mean)*100, 1)

# 5/6 Credible Intervals
round(t(apply(forecast, 2, quantile, c(1/12, 11/12)))*100, 1)


# RMSE in Text

# 2017 Election results in the same order

election_res <- c(32.9, 20.5, 9.2, 8.9, 10.7, 12.6, 5)


round(sqrt(mean((apply(forecast, 2, mean)*100 - election_res)^2)), 2)
```

### Probabilities in Text

```{r Probabilities in Text}
# Probabilities in text

# Probability of 7 (counting CDU and CSU as two parties) parties entering parliament
sum(apply(forecast[,1:6] >= 0.05, 1, all)) / nrow(forecast) * 100

# Probability for AfD to become third strongest party
sum(t(apply(-forecast[,1:6], 1, rank))[,6] == 3) / nrow(forecast) * 100

# Probability for Left to become third strongest party
sum(t(apply(-forecast[,1:6], 1, rank))[,3] == 3) / nrow(forecast) * 100

# Probability for Greens to become third strongest party
sum(t(apply(-forecast[,1:6], 1, rank))[,4] == 3) / nrow(forecast) * 100

# Probability for FDP to become third strongest party
sum(t(apply(-forecast[,1:6], 1, rank))[,5] == 3) / nrow(forecast) * 100

# Coalition Probabilities

coa_df <- forecast

# Set share of parties below 5-percent-threshold to 0

coa_df[coa_df[,1:6] < 0.05] <- 0


# Majority for Grand Coalition? 
# (When coalition vote share is greater than half of the sum of the vote shares
# of parties anbove the 5% thershold.)

gc <- (coa_df[,1] + coa_df[,2]) > (apply(coa_df[,1:6], 1, sum) / 2)

sum(gc) / nrow(forecast) * 100

# Majority for Jamaica Coalition?

jam <- (coa_df[,1] + coa_df[,4] + coa_df[,5]) > (apply(coa_df[,1:6], 1, sum) / 2)

sum(jam) / nrow(forecast) * 100

# Majority for Black-Yellow?

by <- (coa_df[,1] + coa_df[,5]) > (apply(coa_df[,1:6], 1, sum) / 2)

sum(by) / nrow(forecast) * 100

# Majority for Black-Green?

bg <- (coa_df[,1] + coa_df[,4]) > (apply(coa_df[,1:6], 1, sum) / 2)

sum(bg) / nrow(forecast) * 100

# Majority for Red-Red-Green?

rrg <- (coa_df[,2] + coa_df[,3] + coa_df[,4]) > (apply(coa_df[,1:6], 1, sum) / 2)

sum(rrg) / nrow(forecast) * 100
```


### Figure 1

```{r Figure 1}
source("code/R/Figure1.R")
```

### Figure 2

```{r Figure 2}
source("code/R/Figure2.R")
```

## Replication - Supplementary Material - Germany

### B.1.2 Figure 1

```{r B.1.2 Figure 1}
source("code/R/Figure1B12.R")
```

### B.1.3 Figure 2

```{r B.1.3 Figure 2}
source("code/R/Figure2B13.R")
```

### B.2 Figure 3

```{r B.2 Figure 3}
source("code/R/Figure3B2.R")
```

### B.3.1 Table 1

```{r B.3.1 Table 1}
source("code/R/Table1B31.R")
```

### B.3.2 Table 2

```{r B.3.2 Table 2}
source("code/R/Table2B32.R")
```

### B.3.3 Table 3

```{r B.3.3 Table 3}
source("code/R/Table3B33.R")
```

### B.3.4 Table 4

```{r B.3.4 Table 4}
source("code/R/Table4B34.R")
```

## Replication - Supplementary Material - New Zealand

### Forecast and RMSE in Text (C.1)

```{r C.1 Forecast and RMSE}
df <- readRDS(file="output/nz/draws/combined_model/draws_forcast_levels_2017_2.RDS")

forecast <- df$forecast

adjustOrder <- match(c("nat", "lab", "gre", "nzf", "oth"), df$party_names)


forecast <- forecast[,adjustOrder]


# Party Names

plot_names <- c("National", "Labour", "Green", "NZ First", "Others")

df_forecast <- data.frame(y = apply(forecast, 2,  mean),
                          ci = t(apply(forecast, 2, function(x) quantile(x, c(1/12, 11/12)))),
                          ci95 = t(apply(forecast,2, function(x) quantile(x, c(0.025, 0.975)))))

rownames(df_forecast) <- plot_names
colnames(df_forecast) <- c("value", "low", "high", "low95", "high95")

df_forecast <- round(df_forecast*100, 1)

# Numbers in text

df_forecast

round(sqrt(mean((round(df_forecast,1)[,1] -  c(44.45, 36.89, 6.27, 7.2, 5.19))^2)),2)

# Quantities of Interest in text

# Probability of National becoming strongest party
round(sum(t(apply(-forecast[,1:5], 1, rank))[,1] == 1) / nrow(forecast) * 100, 1)

# Probability for Greens to clear the 5 percent threshold
round(sum(forecast[,3] >= 0.05)  / nrow(forecast) * 100, 1)

# Probability for NZ First to clear the 5 percent threshold
round(sum(forecast[,4] >= 0.05)  / nrow(forecast) * 100, 1)
```

### C.1 Figure 4

```{r C.1 Figure 4}
source("code/R/Figure4C1.R")
```

### C.1 Figure 5

```{r C.1 Figure 5}
source("code/R/Figure5C1.R")
```

### C.2.2 Figure 6

```{r}
source("code/R/Figure6C22.R")
```

### C.2.3 Figure 7

```{r}
source("code/R/Figure7C23.R")
```

### C.3 Figure 8

```{r}
source("code/R/Figure8C3.R")
```

### C.4.1 Table 5

```{r}
source("code/R/Table5C41.R")
```

### C.4.2 Table 6

```{r}
source("code/R/Table6C42.R")
```

